A Unification of Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-01-25 colt-21/cvx-flats.tex
Appendix meddling; removed the Lemma formerly known as 27 about equivalence of feasible subspaces for level sets that are projection

We consider supervised learning problems in the space $\X \times \Y$, for some \emph{feature space} $\X$ and a \emph{label space} $\Y$ of size $n$, with data drawn from a distribution $D$ over $\X \times \Y$.
The task is to produce a hypothesis $f: \X \to \R$, for some \emph{prediction space} $\R$, which may be different from $\Y$.
For example, in ranking problems, $\R$ may be all $n!$ permutations over the $n$ labels forming $\Y$.
As we focus heavily on conditional distributions $p := D_x = \Pr[Y|X=x]$ over $\Y$ given some $x \in X$, we often abstract away $x$, working directly with distributions over outcomes $\P \subseteq \simplex$, through tools such as calibration~\cite[Chapter 3]{steinwart2008support}.

@@

\section{Omitted Proofs}\label{app:omitted-proofs}

\subsection{Coping with links for elicitable set-valued properties}
A hyperplane weakly separates two sets if its two closed halfspaces respectively contain the two sets.
\begin{lemma}\label{lem:intersect-levelsets}
	If $\gamma: \P \toto \R$ is an elicitable property, then for any pair of predictions $r, r' \in \R$ where $\gamma_r \neq \gamma_{r'}$, there is a hyperplane $H = \{x \in \reals^{\Y} : v \cdot x = 0\}$, for some $v \in \reals^\Y$, that weakly separates $\gamma_r$ and $\gamma_{r'}$ and has $\gamma_r \cap H = \gamma_{r'} \cap H = \gamma_r \cap \gamma_{r'}$.
\end{lemma}
\begin{proof}
	\btw{Bo: the proof holds as written for the case where the level sets have empty intersection.}
	Let $\ell$ elicit $\gamma$.
	Let $v = \ell(r, \cdot) - \ell(r', \cdot)$, interpreted as a nonzero vector in $\reals^\Y$.
	Let $H = \{ q : v \cdot q = 0 \}$.
	If $v \cdot q < 0$, then $r'$ cannot be optimal, so $q \not\in \gamma_{r'}$.
	So $\gamma_{r'} \subseteq \{ q : v \cdot q \geq 0 \}$.
	Symmetrically, $\gamma_r \subseteq \{ q : v \cdot q \leq 0 \}$.
	This is weak separation, and it immediately implies that $\gamma_r \cap \gamma_{r'} \subseteq H$.
	Finally, if and only if $v \cdot q = 0$, i.e. $q \in H$, by definition the expected losses of both reports are the same.
	So $q \in \gamma_r \cap H \iff q \in \gamma_{r'} \cap H$.
	This gives $\gamma_r \cap H = \gamma_{r'} \cap H = \gamma_r \cap \gamma_{r'} \cap H = \gamma_r \cap \gamma_{r'}$.
\end{proof}

Throughout, given a distribution $p$ and set $P$ \jessiet{not necessarily a subspace, since $F$ isn't a subspace, but $P$ not necessarily convex...} $P$, we defined $P_p := P - \{p\}$ and $\Scr_P(p) := \spn(P_p)$.
\jessiet{Get rid of this notation?}
\jessiet{One extra step to show $\Sc_F(p) = \spn(F_p)$ maybe?}

\begin{lemma}\label{lem:finite-relint-dim}
  Let the $d$-flat $F\subseteq \P$ (defined over finite $\Y$) contain some $p\in\relint{\P}$.
  Then 
  \begin{enumerate}
  	\item[(i)] $p \in \relint{F}$; 
  	\item[(ii)] $\dim(\Scr_F(p)) \geq \dim(\Scr_\P(p)) - d$.
  \end{enumerate}
\end{lemma}
\begin{proof}
  %\raf{Moved; see margin comment:  for the function $W : \Y \to \reals^d$ such that $F = \zeros{W}$.  (Such a function must exist by $F$ being a $d$-flat.)}

@@

  (i)
  Since $p \in \relint{\P}$, for all $q \in \P$, there is some small enough $\epsilon > 0 $ so that for all $\alpha \in (-\epsilon,\epsilon)$, the point $q_\alpha := p - \alpha(q - p)$ is still in $\P$.
  \jessiet{Probably a dumb question, but does this require $\P$ convex?}
  In particular, for $q \in F$, we claim $q_\alpha \in F$.
  %\raft{$V$ comes out of nowhere here, and then in the next bullet you introduce $W$ for the same thing. Better to do all that before both bullets. ``As $F$ is a $d$-flat, we have some $W$... $F=\zeros{W}$''.  Also, okay to just write $\E_p W$ not $\E_p W(Y)$, since technically $W$ is a random variable.}
  As $p,q \in F$, we have $\E_pW = \E_qW = \vec 0$.
  By linearity of expectation, we then have $\E_{q_\alpha} W = \vec 0$.
  % (Y) = \E_p V(Y) - \alpha(\E_q V(Y) - \E_p V(Y)) = \vec 0 - \alpha(\vec 0 - \vec 0) = \vec 0$.
  This implies $q_\alpha \in F$, and therefore $p \in \relint{F}$.

  (ii)
  We first show $\Scr_F(p) = \ker(T_W)$.
%  Let $v \in \ker(T_W)$. % = \{v \in \spn(\P_p) : T_W(v) = \vec 0\}$.
%  From (i), as $p \in \relint{\P}$, we have $\vec 0 \in \relint{F_p}$.
%  Thus there is some $\epsilon > 0$ so that $\epsilon v \in F_p$ and $-\epsilon v \in F_p$.
%  As $\epsilon v \in F_p$, and $v$ is a scalar multiple of it, we additionally conclude $v \in \spn(F_p)$.
%  Moreover, we have $\pm \epsilon v \in \ker(T_W)$ by linearity of expectation, so $v \in \relint{\ker(T_W)}$.
%  Hence, $\spn(F_p) = \ker(T_W)$.\jessie{Right?}\raf{Why? Hint: you want to show $v$ is in the span of $F_p$; in fact, it's a scalar multiple of something in $F_p$.}
%  
%  
  Let $v \in \Scr_F(p)$.
  Then there is some $\alpha$ so that $\alpha v \in F_p$.
  This means $\E_{\alpha v} W = \vec 0$, which in turn implies $\alpha v \in \ker(T_W)$.
  By linearity of expectation, we additionally have $v \in \ker(T_W)$.
  Thus, $\Scr_F(p) \subseteq \ker(T_W)$.

  Now let $v \in \ker(T_W)$, and $v' \in F_p$.
  This means $\E_v W = \vec 0$, so it suffices to show $v = c v' \in F_p$, thus showing $v \in \spn(F_p)$.
  Since $p \in \relint{\P}$, we must have $\vec 0 \in \relint{F_p}$, so we know there is some small enough $\epsilon > 0$ so that $-\alpha v' \in F_p$ for $\alpha \in (-\epsilon, \epsilon)$.
  Take $c = -\alpha$, and we conclude $v \in \Scr_F(p)$.
  Therefore, $\ker(T_W) = \Scr_F(p)$.

  As $\Y$ is a finite set, $\Scr_\P(p)$ is a finite-dimensional vector space.
  The rank-nullity theorem states $\dim(\im(T_W)) + \dim(\ker(T_W)) = \dim(\Scr_\P(p))$.
  As $\dim(\im(T_W)) \leq d$, and we have shown above that $\Scr_F(p) = \ker(T_W)$, the conclusion follows.\raft{Worth checking the diff for what I changed. Inequality was backwards :-)} \jessiet{Lol saw this comment in the diff before I pulled...}
  % 
  %	Now let $v \in \ker(T_W) = \{v \in \spn(\P_p) : T_W(v) = \vec 0\}$.
  %	There must exist an $\epsilon > 0$ so that $\epsilon v \in F_p$ and $-\epsilon v \in F_p$ $p \in \relint{\P}$ implies $\vec 0 \in \relint{F_p}$ by (1.).
  %	Moreover, we have $\pm \epsilon v \in \ker(T_W)$ by linearity of expectation, so $v \in \relint{\ker(T_W)}$.
  %	This allows us to conclude $\spn(F_p) = \ker(T_W)$.\jessie{Right?}
  %	
  %	We want to show $F_p = \P_p \cap \ker(T_W)$, then derive the result from there. \jessie{I don't see why this is necessary.}
  %	
  %	In order to see this, consider $v \in F_p \iff v + p \in F$, and similarly for $\P_p$.
  %	Now, as $F \subseteq \P$ by construction, we have $F_p \subseteq \P_p$, and since $\spn(F_p) = \ker(T_W)$, we additionally have $F_p \subseteq \ker(T_W)$, yielding $F_p \subseteq \P_p \cap \ker(T_W)$.
  %	Now consider $v \in \P_p \cap \ker(T_W)$; we know that $\E_v W = \vec 0$, and therefore, $\E_{q} W = \vec 0$, so $v \in F_p$, thus $F_p = \P_p \cap \ker(T_W)$.
  %	
  %	Since $\spn(F_p) = \ker(T_W)$, we have $\dim(\spn(F_p)) = \dim(\ker(T_W)) \geq \dim(\spn(\P_p)) - d$ by \jessie{isomorphism theorem} since $F_p = \ker(T_W) \cap \P_p$. \jessie{??}
\end{proof}

@@

\subsection{Reconstructing the result of~\citet[Theorem 16]{ramaswamy2016convex}}
%\begin{lemma}\label{lem:feas-sub-is-a-flat}
%	Suppose we have the discrete elicitable property $\gamma$ and distribution $p \in \relint{\simplex}$ with $r \in \gamma(p)$.
%	If $F$ is a flat so that $p \in F \subseteq \gamma_r$, then $F' := F - \{p\}$ is contained in $\Sc_{\gamma_r}(p)$.
%	%  \raf{I think you want $p$ in the interior of the simplex for now}
%\end{lemma}
%\begin{proof} \jessie{Better to combine; not currently using this}
%	We aim to show $v \in F' \implies v \in \Sc_{\gamma_r}(p)$.
%	First, observe $v \in F' \iff p + v \in F$.
%	As $p \in \relint{\simplex}$, by Lemma~\ref{lem:finite-relint-dim}, we additionally have $p \in \relint{F}$, and in turn $\vec 0 \in \relint{F'}$.
%	
%	Suppose $v \in F'$, and since $p \in \relint{F}$, there is an $\epsilon > 0$ so that for all $\alpha \in (-\epsilon, \epsilon)$, we have $p + \alpha v \in F \implies p + \alpha v \in \gamma_r$, since $F$ is convex.%, as are level sets of elicitable properties~\cite{lambert2009eliciting}.
%	The result follows by applying the definition of Feasible Subspaces.
%	%By definition of $\Sc_{\gamma_r}(p)$, there is then an $\epsilon$ satisfying the requirement for $v \in \Sc_{\gamma_r}(p)$, so we can conclude $v \in \Sc_{\gamma_r}(p)$, yielding the desired result.
%	
%% %commented out 01.21.2021 - Jessie
%%	\jessie{Revisit this proof}
%%	Observe $F-p$ is a subspace as it is a linear shift of $F$, which is a linear subspace by definition of a flat and the fact that it contains $\vec 0$ (since $F$ contains $p$, which we subtract from).
%%	Now consider $v \in F - p$.
%%	Since $p \in \relint{\P}$, there is an open ball of radius $\epsilon$ in the span of $\P$ so that for all $q \in B(p, \epsilon)$, we have $q \in \P$.
%%	In particular, take $\alpha = \epsilon / 2$, and we observe $p \pm \alpha v \in B(p, \epsilon)$, and therefore $p \pm \alpha v \in \P$.
%%	Moreover, by the assumption $v \in F - p$, we also have $p \pm \alpha v \in \gamma_r$. 
%%	Since level sets of elicitable properties are convex (\citep{lambert2009eliciting}) this is true for all $\alpha' \in [0,\alpha]$.
%%	Therefore, we observe $v \in S_{\gamma_r}(p)$, so $F-p \subseteq S_{\gamma_r}(p)$.
%\end{proof}

The next result helps us generalize Lemma~\ref{lem:finite-relint-dim} to any $p$; not just to $p \in \relint{\P}$.\jessie{Just for their corollary though...}
\newcommand{\simplexp}{\Delta_{\Y'}}
\jessiet{Are you suggesting getting rid of this Lemma?  This is mostly important for project down to subsimplices of lower support.  The result isn't super obvious to me, but that could just be me. :shrugs:}
\begin{lemma}\label{lem:p-boundary-fsd}
	For any $p \in \P$ and $r$ such that $p \in \gamma_r$, take $\Y' := \supp(p)$.
	Define $\gamma' : \P \toto \R$ with $\gamma' : q \mapsto \gamma(q) \cap \simplexp$.
	Then $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p)$.
\end{lemma}
\begin{proof}
	Consider the ambient space of both $\Sc_{\gamma_r}(p)$ and $\Sc_{\gamma'_r}(p)$ is $\reals^\Y$.
	We trivially have $\dim(\Sc_{\gamma_r}(p)) \geq \dim(\Sc_{\gamma'_r}(p))$ since $\gamma'$ is simply $\gamma$ projected down to an affine subspace of $\reals^\Y$.

	Now to see $\dim(\Sc_{\gamma_r}(p)) \leq \dim(\Sc_{\gamma'_r}(p))$, it suffices to show subset inclusion.
	Take some $v \not \in \Sc_{\gamma'_r}(p)$.
	Observe that $\gamma'_r = \gamma_r \cap \simplexp$, so if $q^\pm := p \pm \epsilon v \not \in \gamma'_r$ for all $\epsilon > 0$ (i.e. $p \not \in \relint{\simplexp}$), it is either because one of $q^+$ or $q^-$ is not in $\gamma_r$ or because either $q^\pm \not \in \simplexp$.
	The first case can be seen easily by the definition of $\gamma'$, and the latter can be seen because leaving $\simplexp$ means one of $q^\pm$ also is not in $\P$, and therefore not in $\gamma_r$ as $\gamma_r \subseteq \P$.
	Thus $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p)$.
	%commented out 05.26.2020
	%	For simplicity, consider $\epsilon = \epsilon_0 / 2$.
	%	Consider $P := \spn(\{e_y : y \in \supp(p) \})$.
	%	\begin{align*}
	%	\dim(\Sc'_{\gamma_r}(p)) &= \dim(\Sc_{\gamma_r}(p)) + \dim(P) - \dim(\Sc_{\gamma_r}(p) + P)
	%	\end{align*}
	%	If $\dim(P) = \dim(\Sc_{\gamma_r}(p) + P)$, the claim holds.
	%	Be definition of $P$, we know $\dim(P) = \|p\|_0$, so we can show $\dim(\Sc_{\gamma_r}(p) + P) = \|p\|_0$.		
	%	One way to do this is to show $\Sc_{\gamma_r}(p) \subseteq P$.
	%	
	%	Suppose there was some $v \not\in P$ such that $v \in \Sc_{\gamma_r}(p)$.
	%	That means there is some $i$ so that $i \not \in \supp(p)$ (i.e. $p_i = 0$) but $v_i \neq 0$. \jessiet{Check this line.}
	%	However, if $v \in \Sc_{\gamma_r}(p)$, then there is some $\epsilon_0 > 0$ so that $p + \epsilon v$ and $p - \epsilon v \in \gamma_r \subseteq \simplex$ for all $\epsilon \in (0, \epsilon_0)$.
	%	For simplicity, consider $\epsilon = \epsilon_0 / 2$.
	%	Since $p_i = 0$, this gives $(p+\epsilon v)_i = (\epsilon v)_i$, and likewise for $(p - \epsilon v)_i$.
	%	As neither $\epsilon$ nor $v_i$ are $0$, one of these terms must be negative, and therefore not in the simplex.
	%	As $\gamma_r \subseteq \simplex$, we then have $v \not \in \Sc_{\gamma_r}(p)$.
	%	Therefore, $\Sc_{\gamma_r}(p) \subseteq P$, and $\dim(\Sc_{\gamma_r}(p) + P) = \dim(P) = \|p\|_0$.
\end{proof}

>>>>

We consider supervised learning problems in the space $\X \times \Y$, for some \emph{feature space} $\X$ and a \emph{label space} $\Y$ of size $n$, with data drawn from a distribution $D$ over $\X \times \Y$.
The task is to produce a hypothesis $f: \X \to \R$, for some \emph{prediction space} $\R$, which may be different from $\Y$.
For example, in ranking problems, $\R$ may be all $n!$ permutations over the $n$ labels forming $\Y$.
As we focus heavily on conditional distributions $p := D_x = \Pr[Y|X=x]$ over $\Y$ given some $x \in X$, we often abstract away $x$, working directly with a convex set of distributions over outcomes $\P \subseteq \simplex$, through tools such as calibration~\cite[Chapter 3]{steinwart2008support}.

@@

\section{Omitted Proofs}\label{app:omitted-proofs}
\subsection{Reconstructing the result of~\citet[Theorem 16]{ramaswamy2016convex}}

A hyperplane weakly separates two sets if its two closed halfspaces respectively contain the two sets.
\begin{lemma}\label{lem:intersect-levelsets}
	If $\gamma: \P \toto \R$ is an elicitable property, then for any pair of predictions $r, r' \in \R$ where $\gamma_r \neq \gamma_{r'}$, there is a hyperplane $H = \{x \in \reals^{\Y} : v \cdot x = 0\}$, for some $v \in \reals^\Y$, that weakly separates $\gamma_r$ and $\gamma_{r'}$ and has $\gamma_r \cap H = \gamma_{r'} \cap H = \gamma_r \cap \gamma_{r'}$.
\end{lemma}
\begin{proof}
	\btw{Bo: the proof holds as written for the case where the level sets have empty intersection.}
	Let $\ell$ elicit $\gamma$.
	Let $v = \ell(r, \cdot) - \ell(r', \cdot)$, interpreted as a nonzero vector in $\reals^\Y$.
	Let $H = \{ q : v \cdot q = 0 \}$.
	If $v \cdot q < 0$, then $r'$ cannot be optimal, so $q \not\in \gamma_{r'}$.
	So $\gamma_{r'} \subseteq \{ q : v \cdot q \geq 0 \}$.
	Symmetrically, $\gamma_r \subseteq \{ q : v \cdot q \leq 0 \}$.
	This is weak separation, and it immediately implies that $\gamma_r \cap \gamma_{r'} \subseteq H$.
	Finally, if and only if $v \cdot q = 0$, i.e. $q \in H$, by definition the expected losses of both reports are the same.
	So $q \in \gamma_r \cap H \iff q \in \gamma_{r'} \cap H$.
	This gives $\gamma_r \cap H = \gamma_{r'} \cap H = \gamma_r \cap \gamma_{r'} \cap H = \gamma_r \cap \gamma_{r'}$.
\end{proof}

Throughout, given a point (typically a distribution) $p$ and convex set $P$, we define $P_p := P - \{p\}$.
\jessiet{Get rid of this notation?}

\begin{lemma}\label{lem:finite-relint-dim}
  Let the $d$-flat $F\subseteq \P$ (defined over finite $\Y$) contain some $p\in\relint{\P}$.
  Then 
  \begin{enumerate}
  	\item[(i)] $p \in \relint{F}$; 
  	\item[(ii)] $\Scr_F(p) = \spn(F_p)$ and $\dim(\Scr_F(p)) \geq \dim(\spn(\P_p)) - d$.
  \end{enumerate}
\end{lemma}
\jessiet{Bo had a good point that $\spn(F_p)$ is probably easier to understand, instead of having an extra layer of notation in there.  Do we want to stick with $\Scr_F(p)$ or $\spn(F_p)$?}
\begin{proof}
  %\raf{Moved; see margin comment:  for the function $W : \Y \to \reals^d$ such that $F = \zeros{W}$.  (Such a function must exist by $F$ being a $d$-flat.)}

@@

  (i)
  Since $p \in \relint{\P}$, for all $q \in \P$, there is some small enough $\epsilon > 0 $ so that for all $\alpha \in (-\epsilon,\epsilon)$, the point $q_\alpha := p - \alpha(q - p)$ is still in $\P$.
  In particular, for $q \in F$, we claim $q_\alpha \in F$.
  %\raft{$V$ comes out of nowhere here, and then in the next bullet you introduce $W$ for the same thing. Better to do all that before both bullets. ``As $F$ is a $d$-flat, we have some $W$... $F=\zeros{W}$''.  Also, okay to just write $\E_p W$ not $\E_p W(Y)$, since technically $W$ is a random variable.}
  As $p,q \in F$, we have $\E_pW = \E_qW = \vec 0$.
  By linearity of expectation, we then have $\E_{q_\alpha} W = \vec 0$.
  % (Y) = \E_p V(Y) - \alpha(\E_q V(Y) - \E_p V(Y)) = \vec 0 - \alpha(\vec 0 - \vec 0) = \vec 0$.
  This implies $q_\alpha \in F$, and therefore $p \in \relint{F}$.

  (ii)
  We first show $\spn(F_p) = \Scr_F(p)$.
  First, take $v \in \Scr_F(p)$, and take $\epsilon_0$ as in the definition.
  For $\epsilon = \epsilon_0 / 2$, we then have $p + \epsilon v \in F \implies \epsilon v \in F_p$, and therefore, $v \in \spn(F_p)$.  
  Now take $v \in \spn(F_p)$.
  Since $p \in \relint{F}$ (i), we have $\vec 0 \in \relint{F_p}$.
  Therefore there is an $\epsilon_0 > 0$ so that $\epsilon v \in F_p$ for all $\epsilon \in (-\epsilon_0, \epsilon_0)$ by convexity of $F$.
  Therefore, $v \in \Scr_F(p)$, and the equality follows.

  We now show $\Scr_F(p) = \ker(T_W)$.
%  Let $v \in \ker(T_W)$. % = \{v \in \spn(\P_p) : T_W(v) = \vec 0\}$.
%  From (i), as $p \in \relint{\P}$, we have $\vec 0 \in \relint{F_p}$.
%  Thus there is some $\epsilon > 0$ so that $\epsilon v \in F_p$ and $-\epsilon v \in F_p$.
%  As $\epsilon v \in F_p$, and $v$ is a scalar multiple of it, we additionally conclude $v \in \spn(F_p)$.
%  Moreover, we have $\pm \epsilon v \in \ker(T_W)$ by linearity of expectation, so $v \in \relint{\ker(T_W)}$.
%  Hence, $\spn(F_p) = \ker(T_W)$.\jessie{Right?}\raf{Why? Hint: you want to show $v$ is in the span of $F_p$; in fact, it's a scalar multiple of something in $F_p$.}
%  
%  more up to date than above; commented out 1.25.21
%  Let $v \in \Scr_F(p)$.
%  Then there is some $\alpha$ so that $\alpha v \in F_p$.
%  This means $\E_{\alpha v} W = \vec 0$, which in turn implies $\alpha v \in \ker(T_W)$.
%  By linearity of expectation, we additionally have $v \in \ker(T_W)$.
%  Thus, $\Scr_F(p) \subseteq \ker(T_W)$.
%
  Observe that $\Scr_F(p) \subseteq \ker(T_W)$ follows trivially from the definitions of the two functions. 
  Now let $v \in \ker(T_W)$, and $v' \in F_p$.
  This means $\E_v W = \vec 0$, so it suffices to show $v = c v' \in F_p$, thus showing $v \in \Scr_F(p)$.
  Since $p \in \relint{\P}$, we must have $\vec 0 \in \relint{F_p}$, so we know there is some small enough $\epsilon > 0$ so that $-\alpha v' \in F_p$ for $\alpha \in (-\epsilon, \epsilon)$.
  Take $c = -\alpha$, and we conclude $v \in \Scr_F(p)$.
  Therefore, $\ker(T_W) = \Scr_F(p)$.

  As $\Y$ is a finite set, $\spn(\P_p)$ is a finite-dimensional vector space.
  The rank-nullity theorem states $\dim(\im(T_W)) + \dim(\ker(T_W)) = \dim(\spn(\P_p))$.
  As $\dim(\im(T_W)) \leq d$, and we have shown above that $\Scr_F(p) = \ker(T_W)$, the conclusion follows.
  % 
  %	Now let $v \in \ker(T_W) = \{v \in \spn(\P_p) : T_W(v) = \vec 0\}$.
  %	There must exist an $\epsilon > 0$ so that $\epsilon v \in F_p$ and $-\epsilon v \in F_p$ $p \in \relint{\P}$ implies $\vec 0 \in \relint{F_p}$ by (1.).
  %	Moreover, we have $\pm \epsilon v \in \ker(T_W)$ by linearity of expectation, so $v \in \relint{\ker(T_W)}$.
  %	This allows us to conclude $\spn(F_p) = \ker(T_W)$.\jessie{Right?}
  %	
  %	We want to show $F_p = \P_p \cap \ker(T_W)$, then derive the result from there. \jessie{I don't see why this is necessary.}
  %	
  %	In order to see this, consider $v \in F_p \iff v + p \in F$, and similarly for $\P_p$.
  %	Now, as $F \subseteq \P$ by construction, we have $F_p \subseteq \P_p$, and since $\spn(F_p) = \ker(T_W)$, we additionally have $F_p \subseteq \ker(T_W)$, yielding $F_p \subseteq \P_p \cap \ker(T_W)$.
  %	Now consider $v \in \P_p \cap \ker(T_W)$; we know that $\E_v W = \vec 0$, and therefore, $\E_{q} W = \vec 0$, so $v \in F_p$, thus $F_p = \P_p \cap \ker(T_W)$.
  %	
  %	Since $\spn(F_p) = \ker(T_W)$, we have $\dim(\spn(F_p)) = \dim(\ker(T_W)) \geq \dim(\spn(\P_p)) - d$ by \jessie{isomorphism theorem} since $F_p = \ker(T_W) \cap \P_p$. \jessie{??}
\end{proof}

@@

%\begin{lemma}\label{lem:feas-sub-is-a-flat}
%	Suppose we have the discrete elicitable property $\gamma$ and distribution $p \in \relint{\simplex}$ with $r \in \gamma(p)$.
%	If $F$ is a flat so that $p \in F \subseteq \gamma_r$, then $F' := F - \{p\}$ is contained in $\Sc_{\gamma_r}(p)$.
%	%  \raf{I think you want $p$ in the interior of the simplex for now}
%\end{lemma}
%\begin{proof} \jessie{Better to combine; not currently using this}
%	We aim to show $v \in F' \implies v \in \Sc_{\gamma_r}(p)$.
%	First, observe $v \in F' \iff p + v \in F$.
%	As $p \in \relint{\simplex}$, by Lemma~\ref{lem:finite-relint-dim}, we additionally have $p \in \relint{F}$, and in turn $\vec 0 \in \relint{F'}$.
%	
%	Suppose $v \in F'$, and since $p \in \relint{F}$, there is an $\epsilon > 0$ so that for all $\alpha \in (-\epsilon, \epsilon)$, we have $p + \alpha v \in F \implies p + \alpha v \in \gamma_r$, since $F$ is convex.%, as are level sets of elicitable properties~\cite{lambert2009eliciting}.
%	The result follows by applying the definition of Feasible Subspaces.
%	%By definition of $\Sc_{\gamma_r}(p)$, there is then an $\epsilon$ satisfying the requirement for $v \in \Sc_{\gamma_r}(p)$, so we can conclude $v \in \Sc_{\gamma_r}(p)$, yielding the desired result.
%	
%% %commented out 01.21.2021 - Jessie
%%	\jessie{Revisit this proof}
%%	Observe $F-p$ is a subspace as it is a linear shift of $F$, which is a linear subspace by definition of a flat and the fact that it contains $\vec 0$ (since $F$ contains $p$, which we subtract from).
%%	Now consider $v \in F - p$.
%%	Since $p \in \relint{\P}$, there is an open ball of radius $\epsilon$ in the span of $\P$ so that for all $q \in B(p, \epsilon)$, we have $q \in \P$.
%%	In particular, take $\alpha = \epsilon / 2$, and we observe $p \pm \alpha v \in B(p, \epsilon)$, and therefore $p \pm \alpha v \in \P$.
%%	Moreover, by the assumption $v \in F - p$, we also have $p \pm \alpha v \in \gamma_r$. 
%%	Since level sets of elicitable properties are convex (\citep{lambert2009eliciting}) this is true for all $\alpha' \in [0,\alpha]$.
%%	Therefore, we observe $v \in S_{\gamma_r}(p)$, so $F-p \subseteq S_{\gamma_r}(p)$.
%\end{proof}

\newcommand{\simplexp}{\Delta_{\Y'}}

%commenting out 01.25.2021 since we really just need one direction.
%\begin{lemma}\label{lem:p-boundary-fsd}
%	For any $p \in \P$ and $r$ such that $p \in \gamma_r$, take $\Y' := \supp(p)$.
%	Define $\gamma' : \P \toto \R$ with $\gamma' : q \mapsto \gamma(q) \cap \simplexp$.
%	Then $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p)$.
%\end{lemma}
%\begin{proof}
%	Consider the ambient space of both $\Sc_{\gamma_r}(p)$ and $\Sc_{\gamma'_r}(p)$ is $\reals^\Y$.
%	We trivially have $\dim(\Sc_{\gamma_r}(p)) \geq \dim(\Sc_{\gamma'_r}(p))$ since $\gamma'$ is simply $\gamma$ projected down to an affine subspace of $\reals^\Y$.
%	
%	Now to see $\dim(\Sc_{\gamma_r}(p)) \leq \dim(\Sc_{\gamma'_r}(p))$, it suffices to show subset inclusion.
%	Take some $v \not \in \Sc_{\gamma'_r}(p)$.
%	Observe that $\gamma'_r = \gamma_r \cap \simplexp$, so if $q^\pm := p \pm \epsilon v \not \in \gamma'_r$ for all $\epsilon > 0$ (i.e. $p \not \in \relint{\simplexp}$), it is either because one of $q^+$ or $q^-$ is not in $\gamma_r$ or because either $q^\pm \not \in \simplexp$.
%	The first case can be seen easily by the definition of $\gamma'$, and the latter can be seen because leaving $\simplexp$ means one of $q^\pm$ also is not in $\P$, and therefore not in $\gamma_r$ as $\gamma_r \subseteq \P$.
%	Thus $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p)$.
%	%commented out 05.26.2020
%	%	For simplicity, consider $\epsilon = \epsilon_0 / 2$.
%	%	Consider $P := \spn(\{e_y : y \in \supp(p) \})$.
%	%	\begin{align*}
%	%	\dim(\Sc'_{\gamma_r}(p)) &= \dim(\Sc_{\gamma_r}(p)) + \dim(P) - \dim(\Sc_{\gamma_r}(p) + P)
%	%	\end{align*}
%	%	If $\dim(P) = \dim(\Sc_{\gamma_r}(p) + P)$, the claim holds.
%	%	Be definition of $P$, we know $\dim(P) = \|p\|_0$, so we can show $\dim(\Sc_{\gamma_r}(p) + P) = \|p\|_0$.		
%	%	One way to do this is to show $\Sc_{\gamma_r}(p) \subseteq P$.
%	%	
%	%	Suppose there was some $v \not\in P$ such that $v \in \Sc_{\gamma_r}(p)$.
%	%	That means there is some $i$ so that $i \not \in \supp(p)$ (i.e. $p_i = 0$) but $v_i \neq 0$. \jessiet{Check this line.}
%	%	However, if $v \in \Sc_{\gamma_r}(p)$, then there is some $\epsilon_0 > 0$ so that $p + \epsilon v$ and $p - \epsilon v \in \gamma_r \subseteq \simplex$ for all $\epsilon \in (0, \epsilon_0)$.
%	%	For simplicity, consider $\epsilon = \epsilon_0 / 2$.
%	%	Since $p_i = 0$, this gives $(p+\epsilon v)_i = (\epsilon v)_i$, and likewise for $(p - \epsilon v)_i$.
%	%	As neither $\epsilon$ nor $v_i$ are $0$, one of these terms must be negative, and therefore not in the simplex.
%	%	As $\gamma_r \subseteq \simplex$, we then have $v \not \in \Sc_{\gamma_r}(p)$.
%	%	Therefore, $\Sc_{\gamma_r}(p) \subseteq P$, and $\dim(\Sc_{\gamma_r}(p) + P) = \dim(P) = \|p\|_0$.
%\end{proof}
